Final paper: Proving Termination of \texttt{zelda-mosaic} Algorithms under Conditions on the Input

### 2021-04-29 paper/paper.tex
add paper skeleton
- copy report
- add ability to input coq-tex files
- add SO to sources
paper: kill goals/timeline section

\newcommand{\matlab}{MATLAB}
\newcommand{\mmatlab}{\textmu\matlab}
\newcommand{\colorlib}{CoLoR}
\renewcommand{\algorithmiccomment}[1]{\% #1}

@@

\title{Progress Report: Proving Termination of \texttt{zelda-mosaic} Algorithms under Conditions on the Input}

@@

\section{Goals and Timeline}

As we neglected to include them in our original proposal, we now propose the
following goals, taking into consideration the progress that we have made so far
with the project:

\begin{enumerate}

    \item \textbf{Minimum Viable Product}: Successful modelling of a majority of
        the desired features corresponding to matrix operations in \mmatlab\@.
        Given the lack of multi-dimensional matrix libraries in Coq and the
        necessary additions of several features in the Coq standard library,
        this alone would be a notable achievement for us.

    \item \textbf{Desired Goal}: Successful binding of our matrix operations to
        \mmatlab\ statements and expressions, including the ability to evaluate
        programs written in \mmatlab\@. A proof of termination, or sketch of
        one, for our V1 algorithm is provided.

    \item \textbf{Stretch Goal}: All of the above, and the addition of all
        operations used in V2 and V3 algorithms (most notably, for loops that
        increment across a range at varying intervals). Proofs that use
        these features.

\end{enumerate}

Given what we have encountered so far, we propose the following modified
timeline for project completion.

\begin{itemize}
    \item \textbf{03/31/21}: Progress Report Due
    \item \textbf{04/09/21}: Significant progress made on most matrix operations
        and data structures.
    \item \textbf{04/16/21}: Binding \mmatlab\ syntax to operations written
        in Coq; definition of semantics and program evaluator; formal proof
        specification written.
    \item \textbf{04/24/21}: Proof(s) should be written or scope adjusted
        accordingly. All logic should be implemented; edits for readability
        should be the main changes henceforth.
    \item \textbf{04/26/21}: Final Proof Due
    \item \textbf{05/03/21}: Final Paper Due
    \item \textbf{05/05/21}: Final Presentation Delivered
\end{itemize}

We provide the following ``diff'' between the scope of our original project
proposal and our new proposal:
\begin{itemize}
    \item Heightened emphasis on implementation of matrix operations, since they
        are proving to be non-trivial.
    \item Addition of goal tiers.
    \item Discussion on Hoare logic.
\end{itemize}

>>>>

\newcommand{\matlab}{MATLAB}
\newcommand{\mmatlab}{\textmu\matlab}
\newcommand{\colorlib}{CoLoR}
\renewcommand{\algorithmiccomment}[1]{\% #1}
\newcommand{\inputcoq}[1]{\InputIfFileExists{#1.v_tex}{}{\typeout{No file #1.v_tex.}}}

@@

\title{Final paper: Proving Termination of \texttt{zelda-mosaic} Algorithms under Conditions on the Input}

@@
